---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**NOTE: This is a toy package created for my assignment for [STAT 545B](https://stat545.stat.ubc.ca/assignments/assignment-b2/) class. It is not meant to be extensive but rather is used as a practice for building packages.**

# janafactors   

<!-- badges: start -->
<!-- badges: end -->

dplyr's `group_by` and `summarise` functions are often used in conjuction with each other, specifically, finding the mean of a quantitative variable by group. In addition to the summary table provided by these two functions, a boxplot of the quanitative variable by group is often helpful in showing the distribution of the data. This package provides a function, `calculate_groups_mean`, that combines the funcitonality of `group_by` and `summarise` as well as visualization through a boxplot. 

## Installation

You can install janafunctions like so:

```{r}
devtools::install_github("jfosea/janafunctions")
```
  
## Demo

For the demo, I will use data sets from the [datasets](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/00Index.html) package, particularly the *InsectSprays* data set. Here is a preview of the data.

```{r}
library(janafunctions)
library(datasets)
head(InsectSprays)
```

I want to look at the mean number of *counts* grouped by *spray*. And so I will run the following into my function `calculate_group_means`

```{r}
calculate_group_means(InsectSprays, spray, count)
```
