---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

**NOTE: This is a toy package created for my assignment for [STAT 545B](https://stat545.stat.ubc.ca/assignments/assignment-b2/) class. It is not meant to be extensive but rather is used as a practice for building packages.**


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# janafunctions

<!-- badges: start -->
<!-- badges: end -->

## Description

dplyr's `group_by` and `summarise` functions are often used in conjuction with each other, specifically, finding the mean of a quantitative variable by group. In addition to the summary table provided by these two functions, a boxplot of the quanitative variable by group is often helpful in showing the distribution of the data. This package provides a function, `calculate_groups_mean`, that combines the funcitonality of `group_by` and `summarise` as well as visualization through a boxplot. 

## Installation

You can install the released version of janafunctions from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("janafunctions")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("jfosea/janafunctions")
```
## Example

This is a basic example which shows you how to solve a common problem. I will use data sets from the [datasets](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/00Index.html) package, particularly the *InsectSprays* data set. Here is a preview of the data.


```{r}
library(janafunctions)
library(datasets)
head(InsectSprays)
```


I want to look at the mean number of *counts* grouped by *spray*. And so I will run the following into my function `calculate_group_means`

```{r}
calculate_group_means(InsectSprays, spray, count)
```

The results show a `tibble` summary table that contains the means by groups. In addition, the function outputs a boxplot by groups.
